\begin{multicols}{2}
This Section gives an overview of the different strategies we use to implement the query to solve
the problem presented in Section~\ref{sec:example}. All the technical details can be found in
\cite{PhilippeCTS2020:MODELS}. First, the naive implementation is based on its OCL specification.
OCL is a standard for expressing queries, and constraints, on elements of models. It is decomposed
on several parts: first, all belonging comments of a post are recursively obtained, then all their
like is count. From these two information, the score of a post is calculated. This function has a
direct, but inefficient, counterpart. The second implementation, designed on top of Pregel, is based
on graph theory. Here, each element of the model is considered as a single element. The third
implementation works on the MapReduce paradigm: every element of the model, without considering its
type, is associated to a score. To finally obtain a score for a port, these intermediate scores a
merged into a single value. Finally, we implemented two additional approaches by mixing the one 
presented above. Some parts of the naive implementation can be optimized using the Pregel strategy.
Similarly, the MapReduce implementation can be partially replaced by an execution based on the 
graph theory of the Pregel paradigm. We experiment our five parallel implementation of the TTC18 query
(Section~\ref{sec:example}). The experiments have been conducted on a shared memory machine with a 
Intel Core i7-8650U having 8 cores at 1.90GHz and a memory of 32GB. The machine was running Ubuntu
16.04 LTS. We use Java 8, Scala 2.12 with Spark 3.1.0. Each speed-up on Table~\ref{tab:results} is
the mean of a series of 30 measures.
\end{multicols}

\begin{table}[ht]
    \centering
    \resizebox{\textwidth}{!}{
    \begin{tabular}{|c|l|l|l|l|l|c|c|c|c|c|}
        \hline
        & \multicolumn{4}{c|}{Dataset} & \multicolumn{6}{c|}{Speed-up (compared to Naive (Sequential) solution)} \\
        \hline
        & \#users & \#posts & \#comments & \#likes & Naive (Sequential) & Naive (Parallel) & Pregel & MapReduce & OCL + Pregel & MapReduce + Pregel \\
        \hline
        1 & 80 & 554 & 640 & 6 & \textbf{1x} & {\color{red} 0.40x} & {\color{dkgreen} 10.30x} & {\color{dkgreen} 5.82x} & {\color{dkgreen} 9.40x} & {\color{dkgreen} 4.63x} \\
        \hline
        2 & 889 & 1064 & 118 & 24 & \textbf{1x} & {\color{red} 0.39x} & {\color{red} 0.36x} & {\color{red} 0.46x} & {\color{red} 0.44x} & {\color{red} 0.46x} \\
        \hline
        3 & 1845 & 2315 & 190 & 66 & \textbf{1x} & {\color{red} 0.51x} & {\color{red} 0.68x} & {\color{red} 0.85x} & {\color{red} 0.66x} & {\color{red} 0.71x} \\
        \hline
        4 & 2270 & 5056 & 204 & 129 & \textbf{1x} & {\color{red} 0.27x} & {\color{red} 0.35x} & {\color{dkgreen} 2.34x} & {\color{red} 0.15x} & {\color{dkgreen} 2.96x} \\
        \hline
        5 & 5518 & 9220 & 394 & 572 & \textbf{1x} & {\color{dkgreen} 4.25x} & {\color{dkgreen} 5.21x} & {\color{dkgreen} 4.17x} & {\color{dkgreen} 4.68x} & {\color{dkgreen} 4.03x} \\
        \hline
        6 & 10929 & 18872 & 595 & 1598 & \textbf{1x} & {\color{dkgreen} 4.68x} & {\color{dkgreen} 2.83x} & {\color{dkgreen} 2.39x} & {\color{dkgreen} 1.97x} & {\color{dkgreen} 3.91x} \\
        \hline
        7 & 18083 & 39212 & 781 & 4770 & \textbf{1x} & {\color{dkgreen} 4.07x} & {\color{dkgreen} 4.12x} & {\color{dkgreen} 4.58x} & {\color{dkgreen} 5.17x} & {\color{dkgreen} 3.27x} \\
        \hline
        8 & 37228 & 76735 & 1158 & 13374 & \textbf{1x} & {\color{dkgreen} 7.28x} & {\color{dkgreen} 9.52x} & {\color{dkgreen} 7.61x} & {\color{dkgreen} 9.66x} & {\color{dkgreen} 9.22x} \\
        \hline
    \end{tabular}}
    \caption{Speed-up of 5 implementations based on different strategies for the TTC18 query}
    \label{tab:results}
\end{table}